---
title: "WNBA Self-Presentation Data Analysis"
authors: Wil Fisackerly, Alexia Pedo Lopes, Michael Seidman, Dr. Mark Nagel
date: "September 7, 2021"
output:
  html_notebook: default
  pdf_document: default
---

```{r echo=FALSE}
rm(list = ls())

library(here)
library(tidyverse)

```


Let's start by loading in the data

```{r echo=FALSE}

demographics <- read_csv(here("Data","0_Demographics.csv"))

# Clean data and indicate factors

# Clarified position

# demographics$Position[demographics$Position == "F/C"] <- "C/F"
# demographics$Position[demographics$Position == "G/F"] <- "F/G"

demographics$Position[demographics$Position == "F/C"] <- "F"
demographics$Position[demographics$Position == "G/F"] <- "G"
demographics$Position[demographics$Position == "C/F"] <- "C"
demographics$Position[demographics$Position == "F/G"] <- "F"

demographics$Position <- as_factor(demographics$Position)

# Birthday data is not cleaned, however age accomplishes the goal and we may
# look at this further, later

demographics$Nationality <- as_factor(demographics$Nationality)

demographics$`Domestic/International` <-
  as_factor(demographics$`Domestic/International`)

demographics$`Current WNBA Team (or Last)` <-
  as_factor(demographics$`Current WNBA Team (or Last)`)

demographics$`Draft Year` <- as.numeric(demographics$`Draft Year`)

# demographics$`Active/2021`[demographics$`Active/2021` == "Y"] <- "Yes"
# demographics$`Active/2021`[demographics$`Active/2021` == "N"] <- "No"

demographics$`Active/2021` <- as.factor(demographics$`Active/2021`)

demographics$`Played in 2020?`[demographics$`Played in 2020?` == "y"] <- "Yes"
demographics$`Played in 2020?`[demographics$`Played in 2020?` == "N"] <- "No"
demographics$`Played in 2020?`[demographics$`Played in 2020?` == "Y"] <- "Yes"

demographics$`Played in 2020?` <- as_factor(demographics$`Played in 2020?`)

demographics <- filter(demographics, Use < 1)
```

```{r echo=FALSE}
# Reading in coding

coding <- read.csv(here("Data","1_Combined_Coding_NEW.csv")
                    , stringsAsFactors = FALSE, fileEncoding = "latin1"
                   )

# Clean data and Indicate factors

coding$Likes <- as.numeric(coding$Likes)

# coding$`Number of Likes` <- as.numeric(coding$`Number of Likes`) FIX THIS

coding$Step.1[coding$Step.1 == ""] <- NA
coding$Step.1[coding$Step.1 == "no cata"] <- NA
coding$Step.1[coding$Step.1 == "no category"] <- NA
coding$Step.1[coding$Step.1 == "1"] <- "Personal Life" 
coding$Step.1[coding$Step.1 == "2"] <- "Business Life" 
coding$Step.1[coding$Step.1 == "3"] <- "Basketball" 
coding$Step.1[coding$Step.1 == "4"] <- "Other Sport" 
coding$Step.1[coding$Step.1 == "5"] <- "Pop Culture or Landmark" 
coding$Step.1[coding$Step.1 == "6"] <- "Meme"

coding$Step.1 <- as_factor(coding$Step.1)

# Doing the same for step 2

coding$Step.2[coding$Step.2 == "1"] <- "Athlete Action"
coding$Step.2[coding$Step.2 == "2"] <- "Dressed but Posed"
coding$Step.2[coding$Step.2 == "3"] <- "Mixed Message"
coding$Step.2[coding$Step.2 == "4"] <- "Non-Sport Setting"
coding$Step.2[coding$Step.2 == "5"] <- "Femininity"
coding$Step.2[coding$Step.2 == "6"] <- "Sexual"

coding$Step.2 <- as_factor(coding$Step.2)

# Social Cause

coding$Social.Cause[coding$Social.Cause == "Y"] <- "Yes"
coding$Social.Cause[coding$Social.Cause == "y"] <- "Yes"
coding$Social.Cause[coding$Social.Cause == "N"] <- "No"
coding$Social.Cause[coding$Social.Cause == "n"] <- "No"
coding$Social.Cause[coding$Social.Cause == ""] <- NA

coding$Social.Cause <- as_factor(coding$Social.Cause)

coding$Athlete.Appear <- as_factor(coding$Athlete.Appear)

```

```{r echo=FALSE}
merged <- left_join(demographics, coding, by = "Name")

# Let's start with frequency of codes

Step_1_frequencies <- merged %>%
  drop_na(Step.1) %>%
  ggplot(aes(fct_infreq(Step.1))) +
  theme_minimal() +
  geom_bar(fill = "orange", 
           color = "black") +
  geom_text(stat = 'count', aes(label = ..count..), hjust = -1) +
  scale_y_continuous(limits = c(0, 800)) +
  coord_flip () +
  labs(x = "Category", 
       y = "Frequency", 
       title = "Frequency of Main Content in WNBA Instagram Posts")

Step_1_frequencies

Step_1_Proportions <- merged %>%
  drop_na(Step.1) %>%
  ggplot(aes(x = fct_infreq(Step.1), y = prop.table(stat(count)),
             label = scales::percent(prop.table(stat(count))))) +
  theme_minimal() +
  geom_bar(fill = "orange", 
           color = "black", position = "dodge") +
  geom_text(stat = 'count', position = position_dodge(.9), vjust = -.5, size = 3) +
  labs(x = "Category", 
       y = "Proportions", 
       title = "Proportions of Main Content in WNBA Instagram Posts")
  
Step_1_Proportions  

Step_2_merged <- merged %>%
  filter(Step.1 %in% c('Business Life', 'Personal Life')) %>%
  drop_na(Step.2)

Step_2_frequencies <- Step_2_merged %>%
  ggplot(aes(fct_infreq(Step.2))) +
  theme_minimal() +
  geom_bar(fill = "orange", 
           color = "black") +
  geom_text(stat = 'count', aes(label = ..count..), hjust = -1) +
  scale_y_continuous(limits = c(0, 500)) +
  coord_flip () +
  labs(x = "Category", 
       y = "Frequency", 
       title = "Frequency of Self-Presentation in Personal and Business Photos")

Step_2_frequencies

Step_2_Proportions <- Step_2_merged %>%
  ggplot(aes(x = fct_infreq(Step.2), y = prop.table(stat(count)),
             label = scales::percent(prop.table(stat(count))))) +
  theme_minimal() +
  geom_bar(fill = "orange", 
           color = "black", position = "dodge") +
  geom_text(stat = 'count', position = position_dodge(.9), vjust = -.5, size = 3) +
  labs(x = "Category", 
       y = "Proportions", 
       title = "Proportions of Self-Presentation in Personal and Business Photos")
  
Step_2_Proportions 

```

```{r}

# (Pegoraro et al., 2018)

# THIS IS THE FUN STUFF

# Engagement between Step two photos and likes (ANOVA), bivariate correlation
# between likes and type of photos 

Step.2.anova <-
  summary(aov(Likes ~ Step.2, data = Step_2_merged))

Step.2.anova

# Mean likes

aggregate(Step_2_merged$Likes, list(Step_2_merged$Step.2), FUN = mean)

# Tukey comparison

Step.2.tukey <- TukeyHSD((aov(Likes ~ Step.2, data = Step_2_merged)))

Step.2.tukey

# Running a linear model

lm.model <- lm(Step_2_merged$Likes ~ Step_2_merged$Step.2)

summary(lm.model)

# Percent athletes appeared in the photos themselves

# 52.8 business, 36.35 personal, 79.15% photos feature the athletes (INDICATE
# INTERNATIONAL AND DOMESTIC PERCENTAGES)

# t-test to see if when athlete appeared more like. ANOVA checked the number of 
# likes to each type of photo (sexually suggestive)

appear_anova <- merged %>%
  drop_na(Athlete.Appear)

merged <- merged %>%
  drop_na(Likes)

summary(aov(Likes ~ Athlete.Appear, data = appear_anova))

# Running a linear model

lm.model_aa <- lm(appear_anova$Likes ~ appear_anova$Athlete.Appear)

summary(lm.model_aa)

# RUN AN ANALYSIS TO SEE IF NUMBER OF SEASONS/AGE/POSITION/NATIONALITY IMPACTS LIKES (INSTEAD OF GE GENDER
# DIFFERENCES)

```

```{r}
# Running an ANOVA on Step 1 and number of likes

summary(aov(Likes ~ Step.1, data = merged))

# Mean likes of Step 1

aggregate(merged$Likes, list(merged$Step.1), FUN = mean)

# Running a t-test for Domestic/Nationality on Likes

t.test(Step_2_merged$Likes ~ Step_2_merged$`Domestic/International`)

# Not significant (0.218)

# Running an ANOVA on position number of Likes

summary(aov(Likes ~ Position, data = Step_2_merged))

# It is significant! Let's do a Tukey to figure out why

TukeyHSD((aov(Likes ~ Position, data = Step_2_merged)))

aggregate(Step_2_merged$Likes, list(Step_2_merged$Position), FUN = mean)

# Still some NAs here (G)

# Mean age

mean(Step_2_merged$Age)

# GGplot of age/likes

library(ggpubr)

cor.test(Step_2_merged$Age, Step_2_merged$Likes, method = "pearson", use = "complete.obs")

lm(Age ~ Likes, data = Step_2_merged)

Step_2_merged %>%
ggplot(aes(x = Age, y = Likes)) +
  geom_point(alpha = 0.3) +
  scale_y_continuous(trans = "log10") +
 # scale_y_continuous(trans = log2_trans(), breaks = trans_breaks("log", function(x) 2^x), 
  #                   labels = trans_format("log2", math_format(2^.x))) +
  stat_smooth(method = "lm")

```

ANOVA is highly significant, thus the categories in Step 2 are statistically different in their engagement 

# ANOVA WAS CONDUCTED TO COMPARE THE EFFECT OF SELF-PRESENTATION CATEGORIES OF 
# ATHLETES' PHOTOS ON THE NUMBER OF LIKES RECEIVED (I.E. ENGAGEMENT). THERE WAS 
# A SIGNIFICANT DIFFERENCE IN NUMBER OF LIKES RECEIVED ACROSS SELF-PRESENTATION
# CATEGORIES AT THE p < .05 SIGNIFICANCE LEVEL. NOTE: STEP 2 ONLY CATEGORIZES THE
# PICTURES IN WHICH ATHLETES WERE PRESENT



# NEED TO LOOK UP HOW TO REPORT TUKEY'S

# THERE ARE STATISTICALLY SIGNIFICANT DIFFERENCES AT THE p < 0.05 LEVEL BETWEEN
# SEXUAL AND FEMININITY (0.0000), NON-SPORT SETTING AND DRESSED BUT POSED (0.0055),
# SEXUAL AND DRESSED BUT POSED (0.0000), SEXUAL AND MIXED MESSAGE (0.0000), 
# NON-SPORT SETTING AND ATHLETE ACTION (0.0055), SEXUAL AND ATHLETE ACTION (0.0000),
# AND SEXUAL AND NON-SPORT SETTING (0.0000)

# INTERESTINGLY, THE CATEGORY WITH MORE LIKES (I.E., ENGAGEMENT) IS SEXUALLY SUGGESTIVE. # ALONG WITH THAT CATEGORY, FEMINITY AND NON-SPORT SETTING ARE STATISTICALLY SIGNIFICANT # AT THE 0.05 SIGNIFICANCE LEVEL.

# THERE IS A SIGNIFICANT DIFFERENCE AT THE p < .05 LEVEL IN THE NUMBER OF LIKES
# A POST RECEIVES IF THE ATHLETE IS PRESENT (0.0135). A LINEAR MODEL INDICATED 
# THAT THERE IS A NEGATIVE CORRELATION BETWEEN THE ATHLETE NOT APPEARING IN THE
# PHOTO AND THE NUMBER OF LIKES THAT A PHOTO RECEIVES AT THE p < .05 CONFIDENCE
# LEVEL (0.00635).

```{r}

filter(Step_2_merged, Step.2 == "Sexual")

filter(Step_2_merged, Account == "ecambage") %>%
  select(Step.2, Likes)

filter(Step_2_merged, Account == "tea.cooper2") %>%
  select(Step.2, Likes)

```

# CREATE A TABLE FOR MEAN NUMBER OF LIKES FOR EACH CATEGORY (STEP 1 AND 2)

# T-test for only two conditions (i.e. athlete appear)

# Nationality

# Position

```{r}
# ANOVA for Age and Step. 1.

Age.anova <- drop_na(merged)

Age.anova <-
  summary(aov(Age ~ Step.1, data = merged))

Age.anova

# Mean age

Age_means_s1 <- aggregate(merged$Age, list(merged$Step.1), FUN = mean)
Age_sd_s1 <- aggregate(merged$Age, list(merged$Step.1), FUN = sd)
Age_means_s1
Age_sd_s1

# Just ANOVA for personal life and business life

Age_merge.anova <-
  summary(aov(Age ~ Step.1, data = Step_2_merged))

Age_merge.anova

# Tukey comparison

AgeStep.1.tukey <- TukeyHSD((aov(Age ~ Step.1, data = merged)))

AgeStep.1.tukey

# Chi-Square for Nationality and Step. 1.

Nat.cs <- chisq.test(merged$`Domestic/International`, merged$Step.1,)

Nat.cs

NAT_table <- table(merged$`Domestic/International`, merged$Step.1)

# Chi-Square for Age and Step 1.

Pos.cs <- chisq.test(merged$Position, merged$Step.1,)

Pos.cs

POS_table <- table(merged$Position, merged$Step.1)

```

